Sketching for Density Estimation

### 2018-11-09 density.tex
draft

>>>>

\subsection{Another approach}
Considering the view with $\phi$ let us restate the objective. For a point $y$ we wish to estimate
$$ \D(y) = \sum_i K(x_i,y) = \ip{\sum_i  \phi(x_i), \phi(y)} $$
simultaneously for all $y$. We can try to do this with any re-weighting of the $x_i$'s
$$ \sum_i K(x_i,y) \approx \sum_i w_i K(x_i,y) =  \ip{\sum_i w_i \phi(x_i), \phi(y)} $$
while aiming for the $w$ vector to be sparse. Letting $z_i=\phi(x_i)$, $Z$ be the matrix whose columns are $z_i$ and $v=\sum_i z_i$ we have a sparse regression problem with a single data point
$$ \min_w \| Zw -  v\|^2 \ \ \text{s.t.} \|w\|_0 \leq k/2$$
We proved that there exist a solution achieving $\sqrt{k}$. Could we prove that better solutions exist? In one extreme, all $z_i$ are orthogonal (corresponding to vectors that are very far away). Here you cannot achieve more than
